Macroscopic Salt Rejection through Electrostatically Gated Nanoporous Graphene

### 2019-01-17 paper/SI.tex
Add comment CJ & RW about title

\title{Macroscopic Salt Rejection through Electrostatically Gated Porous Graphene}

@@

The conductivity increase $s$ (mS$\cdot$cm$^{-1}\cdot$d$^{-1}$) is
converted into ion permeation rates $\boldsymbol{J}_{\mathrm{PCTE}}$
(mol$\cdot$m$^{-2}\cdot$s$^{-1}$) by use of a calibration factor
$c_{\mathrm{f}}$, the volume of LCR ($V_{\mathrm{LCR}}$) , the area of
the membrane $A$ and the time $t$ as:
\begin{equation}
  \label{eq:JPCTE}
  \boldsymbol{J}_{\mathrm{PCTE}} = \frac{s V_{\mathrm{LCR}}}{c_{\mathrm{f}} A t}
\end{equation}
The calibration factors for all salts have been obtained by a linear
fit of conductivity \textit{versus} concentration for 4 solutions with
concentrations from 10$^{-4}$ M to 10$^{-2}$ M and extracting the
resulting slope. The rest of the factors are $V_{\mathrm{LCR}}$ = 7.33
mL, $A$ = 9$\times$10$^{-6}$ m$^{-2}$. Table \ref{tab:exp-2} shows the
averaged conductivity increase s, the extracted calibration factors
$c_{\mathrm{f}}$ and the resulting ion permeation rates using
Eq. \ref{eq:JPCTE}. The values from this table are shown in main text \Fig 2b
(blue bars).
\begin{table}[htbp]
  \centering
  \begin{tabular}{lccc}
    \hline
    Salt & $s$ (mS$\cdot$cm$^{-1}$d$^{-1}$) & $c_{\mathrm{f}}$ (mS$\cdot$cm$^{-1}\cdot$mol$^{-1}\cdot$ml) &
                                                                                                            $\boldsymbol{J}_{\mathrm{PCTE}}$ (10$^{6}$ mol$\cdot$m$^{-2}\cdot$s$^{-1}$)\\
    \hline
    KCl & 1.51$\pm$0.27$\times$10$^{-2}$  & 106   & 1.34 $\pm$ 0.24\\
    NaCl        & 9.90$\pm$0.17$\times$10$^{-3}$ & 91    & 1.02 $\pm$ 0.02\\
    LiCl        & 6.03 $\pm$0.80$\times$10$^{-3}$        & 83    & 0.682 $\pm$ 0.090\\
    CaCl$_{2}$  & 1.25$\pm$0.1$\times$10$^{-2}$    & 149   & 0.789 $\pm$ 0.063\\
    MgSO$_{4}$  & 8.80$\pm$1.2$\times$10$^{-3}$   & 130   & 0.633 $\pm$ 0.084\\
    K$_{3}$[Fe(CN)$_{6}]$ & 2.40$\pm$0.28$\times$10$^{-2}$   & 395   & 0.575 $\pm$ 0.063\\
    K$_{2}$SO4$_{4}$    & 1.98$\pm$0.20$\times$10$^{-2}$  & 258   & 0.722 $\pm$ 0.073\\
    \hline
  \end{tabular}
  \caption{Extracted slope $s$ as an averaged result from 3 consecutive
    measurements, the calibration factors $c_{\mathrm{f}}$ and the resulting ion
    permeation $\boldsymbol{J}_{\mathrm{PCTE}}$ through b-PCTE membranes for all salts.}
  \label{tab:exp-2}
\end{table}

>>>>

\title{Macroscopic Salt Rejection through Electrostatically Gated Nanoporous Graphene}

@@

The conductivity increase $s$ (mS$\cdot$cm$^{-1}\cdot$d$^{-1}$) is
converted into ion permeation rates $\boldsymbol{J}_{\mathrm{PCTE}}$
(mol$\cdot$m$^{-2}\cdot$s$^{-1}$) by use of a calibration factor
$c_{\mathrm{f}}$, the volume of LCR ($V_{\mathrm{LCR}}$) , the area of
the membrane $A$ and the time $t$ as:
\begin{equation}
  \label{eq:JPCTE}
  \boldsymbol{J}_{\mathrm{PCTE}} = \frac{s V_{\mathrm{LCR}}}{c_{\mathrm{f}} A t}
\end{equation}
The calibration factors for all salts have been obtained by a linear
fit of conductivity \textit{versus} concentration for 4 solutions with
concentrations from 10$^{-4}$ M to 10$^{-2}$ M and extracting the
resulting slope. The rest of the factors are $V_{\mathrm{LCR}}$ = 7.33
mL, $A$ = 9$\times$10$^{-6}$ m$^{-2}$. Table \ref{tab:exp-2} shows the
averaged conductivity increase s, the extracted calibration factors
$c_{\mathrm{f}}$ and the resulting ion permeation rates using
Eq. \ref{eq:JPCTE}. The values from this table are shown in main text \Fig 2b
(blue bars).
\begin{table}[htbp]
  \centering
  \begin{tabular}{lccc}
    \hline
    Salt & $s$ (mS$\cdot$cm$^{-1}$d$^{-1}$) & $c_{\mathrm{f}}$ (mS$\cdot$cm$^{-1}\cdot$mol$^{-1}\cdot$L) &
                                                                                                            $\boldsymbol{J}_{\mathrm{PCTE}}$ (10$^{6}$ mol$\cdot$m$^{-2}\cdot$s$^{-1}$)\\
    \hline
    KCl & 1.51$\pm$0.27$\times$10$^{-2}$  & 106   & 1.34 $\pm$ 0.24\\
    NaCl        & 9.90$\pm$0.17$\times$10$^{-3}$ & 91    & 1.02 $\pm$ 0.02\\
    LiCl        & 6.03 $\pm$0.80$\times$10$^{-3}$        & 83    & 0.682 $\pm$ 0.090\\
    CaCl$_{2}$  & 1.25$\pm$0.1$\times$10$^{-2}$    & 149   & 0.789 $\pm$ 0.063\\
    MgSO$_{4}$  & 8.80$\pm$1.2$\times$10$^{-3}$   & 130   & 0.633 $\pm$ 0.084\\
    K$_{3}$[Fe(CN)$_{6}]$ & 2.40$\pm$0.28$\times$10$^{-2}$   & 395   & 0.575 $\pm$ 0.063\\
    K$_{2}$SO4$_{4}$    & 1.98$\pm$0.20$\times$10$^{-2}$  & 258   & 0.722 $\pm$ 0.073\\
    \hline
  \end{tabular}
  \caption{Extracted slope $s$ as an averaged result from 3 consecutive
    measurements, the calibration factors $c_{\mathrm{f}}$ and the resulting ion
    permeation $\boldsymbol{J}_{\mathrm{PCTE}}$ through b-PCTE membranes for all salts.}
  \label{tab:exp-2}
\end{table}
